HTW E2 Testing

### 2023-10-09 Analysis/e2_test.qmd
automate stats fix

```{r}
#| label: tbl-e2-bmm-dist
#| tbl-cap: "Experiment 2. Bayesian Mixed Model predicting absolute deviation as a function of condition (Constant vs. Varied) and Velocity Band"
#contrasts(test$condit)

# contrasts(testE2$vb)

@@

coef_details <- broom.mixed::tidy(e2_distBMM) |>
  filter(term == "conditVaried") |> 
  select(estimate, conf.low, conf.high) |> mutate(across(where(is.numeric), \(x) round(x, 2)))

>>>>

```{r}
#| label: tbl-e2-bmm-dist
#| tbl-cap: "Experiment 2. Bayesian Mixed Model predicting absolute deviation as a function of condition (Constant vs. Varied) and Velocity Band"
#contrasts(test$condit) 
# contrasts(testE2$vb)

@@

coef_details <- get_coef_details(e2_distBMM, "conditVaried")
